\vskip-0.6in LOBBYING AND LEGISLATIVE UNCERTAINTY

### 2016-02-15 draft.tex
finish model section by turning sec:uncert into text

\subsection{Parameterizing Uncertainty to Vary by Legislator}
\label{sec:uncert}
I'm going to start by changing the uncertainty for just one legislator when there is just one vote buyer (B). I will do this for the legislator at position $-0.5$, which corresponds to $Y$. The FOCs become, for $Z$ (similarly for $X$, and from Equation~\ref{eq:logistic})
	\begin{equation}
		W_B \biggl[ \frac{e^{-X} + e^{-\frac{Y}{s_{-.5}}}}{\left(1+e^{-X}\right)\left(1+e^{-\frac{Y}{s_{-.5}}}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
	\end{equation}
	And for $Y$
  \begin{equation}
		W_B \biggl[ \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-\frac{Y}{s_{-.5}}}}{s_{-.5}\left[1+e^{-\frac{Y}{s_{-.5}}}\right]^2} \biggr]  = 1
	\end{equation}

\vskip.2in
The same thing can be done for the legislator at position $0.5$. The objective function when both vary is
			  \begin{multline}
			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
					W_B \biggl[ \frac{1}{1+e^{-X}} \frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} +
					\frac{1}{1+e^{-X}} \frac{1}{1+e^{-\frac{Z}{s_{.5}}}} + \\
					\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} \frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} - 2	\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
				\end{multline}

\vskip.2in
Now what impact does this have on Vote Buyer B's decisions (in the absence of bribes by Vote Buyer A)?
\begin{itemize}
	\item First, how does the probability that the legislator at $0.5$ (most unfriendly to $B$) votes with $B$ change when $s_{.5}$ goes from 1 to 2 (and there are no bribes)?
		\begin{itemize}
			\item When $s_{.5}$ is 1, the probability is $\frac{1}{1+e^{-\frac{Z}{s_{.5}}}} = \frac{1}{1+e^{-\frac{-.5}{1}}} = \frac{1}{1+e^{.5}} = 0.3775$
			\item When $s_{.5}$ is 2, the probability is $\frac{1}{1+e^{-\frac{Z}{s_{.5}}}} = \frac{1}{1+e^{-\frac{-.5}{2}}} = \frac{1}{1+e^{.25}} = 0.4378$
			\item That is, the probability that the least friendly legislator votes with $B$ \textit{rises}
		\end{itemize}
	\item Now, how does the probability that the legislator at $-0.5$ (most friendly to $B$) votes with $B$ change when $s_{-.5}$ goes from 1 to 2 (and there are no bribes)?
		\begin{itemize}
			\item When $s_{-.5}$ is 1, the probability is $\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} = \frac{1}{1+e^{-\frac{.5}{1}}} = \frac{1}{1+e^{-.5}} = 0.6225$
			\item When $s_{-.5}$ is 2, the probability is $\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} = \frac{1}{1+e^{-\frac{.5}{2}}} = \frac{1}{1+e^{-.25}} = 0.5622$
			\item That is, the probability that the least most legislator votes with $B$ \textit{falls}
		\end{itemize}
	\item Numerical example. Take $\al=0$ and ignore A. Take $s_{-.5}$ from 1 to 2. $B$ stops bribing legislator $-0.5$ (most friendly) altogether.
		\begin{itemize}
			\item This is true even with $s_{-.5}$ as low as 1.2 (taking $s_{.5} = s_{0} = 1$)
			\item For $1 < s_{-.5} < 1.2$, no bribe for $-0.5$ guy until $W_B$ gets significantly higher, and then his net position is lower than $X=Z$
			\item Reverse if $s_{-.5} < 1$: move $-0.5$ guy further left than $X=Z$ (but not further than $X$ when just these two); in some cases leave $0.5$ guy at zero
		\end{itemize}
	\item Numerical example. Take $\al=0$ and ignore A. Take $s_{.5}$ from 1 to 1.5. $B$ stops bribing legislator $0.5$ (least friendly) altogether. Does better in welfare terms because the probability this guy votes in his favor shifts up
		\begin{itemize}
			\item For $s_{.5} = 1.1$, no bribe for $0.5$ guy until $W_B$ gets significantly higher, and then his net position is lower than $X=Y$
			\item At $s_{.5} = .75$: ONLY Z for $W_B \in \left[6,8\right]$ (8 is usually where it's $X$ alone). Then $Z$ and $Y$ together but $Z$ further on net than $Y$. Eventually all three, with $X=Y$, $Z$ further
		\end{itemize}
\end{itemize}

\newpage
\subsection{Intuition}
\begin{itemize}
	\item A legislator votes for $x$ (A's preferred policy, against the status quo) if 
		\[
		  v(z) = \al - \beta z + a(z) - b(z) > 0
		\]
	\item B needs 2 ``no'' votes, or two legislators with $v(z) < 0$. When $a(z) = 0$, this is
		\[
		  \al - \beta z - b(z) < 0
		\]

		\begin{center}
		or 
		\end{center}
		\[
		  \beta z - \al + b(z) > 0
		\]
		\item If $\al > 0$, legislators on average are biased against B.
			\begin{itemize}
				\item If $\al < 0$, legislators on average are biased in favor of B.
				\item If $\al$ is negative enough, bribe only legislator furthest to the left (most against B)
			\end{itemize}
		\item If $X,Y,$ or $Z$ is positive, it means the probability of legislator $0,-\frac{1}{2},$ or $\frac{1}{2}$ voting for the status quo / against the new proposal / with interest group B is greater than $0.5$.
\end{itemize}

\vskip.1in
Recall:
		\begin{enumerate}
			\item $X = -\alpha + b(0)$ 
			\item $Y = \frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$
			\item $Z = -\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$ 
		\end{enumerate}

\vskip.1in
Pattern more or less is to get the guy who is WHAT?
\begin{itemize}
	\item Frank: Imagine a see-saw; these guys are weights on the see-saw.
	\item From looking at overlaided graphs of the pdfs (pdf-graph.R), it appears that the legislator who is chosen first is the one who has the most probability mass just to the left of 0 (it's probability mass to the right of zero that counts for winning the vote).
		\begin{itemize}
			\item But this is not quite right: sometimes the non-negativity constraint binds on the PDF of that variables (as in the case of $\al=-0.3$ and $W_B = 8$.
		\end{itemize}
\end{itemize}

(Remember that I've assumed a very specific functional form)	
\begin{itemize}
	\item use $\al$ in prop:2NNB
\end{itemize}

%If we're going to do an empirical implementation of $\ga$ below, model needs to start with a basic understanding of uncertainty, run through lobbying response to it, up through aggregation into $\ga$ and how lobbying behavior turns into a ``yea'' vote total.

Goal: characterize SPNE in pure strategies

@@

@@

>>>>

\subsection{Varying Uncertainty across Legislators}
\label{sec:uncert}
We allow the amount of uncertainty regarding each legislator's ideal point to vary across legislators by letting the scale parameter of the logistic distribution be different for each legislator. A larger scale parameter is associated with greater variance and thus more uncertainty as to the legislator's ideal point. The objective function for Vote Buyer $B$ becomes
 \begin{multline}
    \max_{b_{-\frac{1}{2}}, b_0, b_{\frac{1}{2}}} 
					W_B \biggl[ \frac{1}{1+e^{-\frac{X}{s_0}}} \frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} +
					\frac{1}{1+e^{-\frac{X}{s_0}}} \frac{1}{1+e^{-\frac{Z}{s_{.5}}}} + \\
					\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} \frac{1}{1+e^{-\frac{Z}{s_{.5}}}} - 2	\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} \frac{1}{1+e^{-\frac{X}{s_0}}} \frac{1}{1+e^{-\frac{Z}{s_{.5}}}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b_j
	\end{multline}

We will see that allowing for this asymmetric uncertainty changes the predictions of the model in important ways. To lay the groundwork for the results to coming in Section~\ref{sec:resunc}, let's look at how the cumulative probabilities change for the most extreme legislators when the mean of their ideal point distribution is fixed but the scale parameter increases.

First, how does the probability that the legislator at $0.5$ (the one who is most unfriendly to $B$) votes with $B$ change when $s_{.5}$ goes from 1 to 2 in the absence of bribes? When $s_{.5}$ is 1, the probability is $\frac{1}{1+e^{-\frac{Z}{s_{.5}}}} = \frac{1}{1+e^{-\frac{-.5}{1}}} = \frac{1}{1+e^{.5}} = 0.3775$. When $s_{.5}$ is 2, the probability is $\frac{1}{1+e^{-\frac{Z}{s_{.5}}}} = \frac{1}{1+e^{-\frac{-.5}{2}}} = \frac{1}{1+e^{.25}} = 0.4378$. That is, the probability that the least friendly legislator votes with $B$ \textit{rises} when the uncertainty surrounding her ideal point increases.

Now, how does the probability that the legislator at $-0.5$ (the one who is most friendly to $B$) votes with $B$ change when $s_{-.5}$ goes from 1 to 2? When $s_{-.5}$ is 1, the probability is $\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} = \frac{1}{1+e^{-\frac{.5}{1}}} = \frac{1}{1+e^{-.5}} = 0.6225$. When $s_{-.5}$ is 2, the probability is $\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} = \frac{1}{1+e^{-\frac{.5}{2}}} = \frac{1}{1+e^{-.25}} = 0.5622$. Here, the probability that the most friendly legislator votes with $B$ \textit{falls} when the uncertainty surrounding her ideal point increases.

@@

Although uncertainty is present in the environment under consideration here, information about that uncertainty is symmetric. Therefore the appropriate equilibrium notion is subgame perfect Nash equilibrium.

@@

\subsection{Intuition}
\begin{itemize}

		\item If $\al > 0$, legislators on average are biased against B.
			\begin{itemize}
				\item If $\al < 0$, legislators on average are biased in favor of B.
				\item If $\al$ is negative enough, bribe only legislator furthest to the left (most against B)
			\end{itemize}
		\item If $X_B,Y_B,$ or $Z_B$ is positive, it means the probability of legislator $0,-\frac{1}{2},$ or $\frac{1}{2}$ voting for the status quo / against the new proposal / with interest group B is greater than $0.5$.
\end{itemize}

\vskip.1in
Pattern more or less is to get the guy who is WHAT?
\begin{itemize}
	\item From looking at overlaided graphs of the pdfs (pdf-graph.R), it appears that the legislator who is chosen first is the one who has the most probability mass just to the left of 0 (it's probability mass to the right of zero that counts for winning the vote).
		\begin{itemize}
			\item But this is not quite right: sometimes the non-negativity constraint binds on the PDF of that variables (as in the case of $\al=-0.3$ and $W_B = 8$.
		\end{itemize}
\end{itemize}

\subsection{Varying Uncertainty across Legislators}
\label{sec:resunc}
Numerical example. Take $\al=0$ and ignore A. Take $s_{.5}$ from 1 to 1.5. $B$ stops bribing legislator $0.5$ (least friendly) altogether. Does better in welfare terms because the probability this guy votes in his favor shifts up
		\begin{itemize}
			\item For $s_{.5} = 1.1$, no bribe for $0.5$ guy until $W_B$ gets significantly higher, and then his net position is lower than $X=Y$
			\item At $s_{.5} = .75$: ONLY Z for $W_B \in \left[6,8\right]$ (8 is usually where it's $X$ alone). Then $Z$ and $Y$ together but $Z$ further on net than $Y$. Eventually all three, with $X=Y$, $Z$ further
		\end{itemize}
Numerical example. Take $\al=0$ and ignore A. Take $s_{-.5}$ from 1 to 2. $B$ stops bribing legislator $-0.5$ (most friendly) altogether.
		\begin{itemize}
			\item This is true even with $s_{-.5}$ as low as 1.2 (taking $s_{.5} = s_{0} = 1$)
			\item For $1 < s_{-.5} < 1.2$, no bribe for $-0.5$ guy until $W_B$ gets significantly higher, and then his net position is lower than $X=Z$
			\item Reverse if $s_{-.5} < 1$: move $-0.5$ guy further left than $X=Z$ (but not further than $X$ when just these two); in some cases leave $0.5$ guy at zero
		\end{itemize}
